Chapter 2 Draft

### 2020-05-26 Rmd/Quantitative_Data_Models_plot.Rmd
models

>>>>

model_5 <- readRDS("Data/RData/model_5_visits_plant_height_5.rds")
pred <- readRDS("Data/RData/pred_plot_visits_plant_height_5.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_plant_height_5.rds")

mydf <- ggpredict(model_5, terms = c("plant_height_mean_m"))
plant_height_5 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("Plant height (m)") + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted closeness") + geom_point(data= all_tf, aes(x =plant_height_mean_m , y = pred))+
  geom_line( alpha = 1, fill=c("blue", "red", "green"))+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

model_5 <- readRDS("Data/RData/model_5_visits_style_length_5.rds")
pred <- readRDS("Data/RData/pred_plot_visits_style_length_5.rds")
all_tf <- readRDS("Data/RData/data_plot_visits_style_length_5.rds")

mydf <- ggpredict(model_5, terms = c("style_length_mm"))
style_length_5 <- ggplot(mydf, aes(x = x, y = predicted)) + xlab("style_length (mm)")  + theme_ds4psy() + theme(legend.position = "none") + ylab("Predicted closeness") + geom_point(data= all_tf, aes(x =style_length_mm , y = pred))+
  geom_line( alpha = 1)+ geom_ribbon(aes(x = x,ymin = conf.low, ymax = conf.high, fill = group), alpha = 0.1, colour = NA)

p <- plot_grid(plant_height_5,style_length_5, NULL, ncol = 2)
